Integrated multi-omics analysis reveals Lactobacillus anti-inflammatory process in vaginal tissue

### 2021-02-15 reports/rmarkdown/manuscript/manuscript_template.tex
fixes plots and adds picrust

\title{Integrated multi-omics analysis reveals Lactobacillus anti-inflammatory process in vaginal tissue}
\usepackage{etoolbox}
\makeatletter
\providecommand{\subtitle}[1]{% add subtitle to \maketitle
  \apptocmd{\@title}{\par {\large #1 \par}}{}{}
}
\makeatother
\subtitle{A demonstration of Rmarkdown using Herman Bumpus' data}
\author{Author One\textsuperscript{1},
Author Two\textsuperscript{2},
Author Three\textsuperscript{1,2}}
\date{January 15, 2021}

@@

To understand the longitudinal and tissue-specific microbiome profile in vaginal samples, 113 adult female sex workers were enrolled in {[}\ldots{]}. Among those, 14 were previously tested positive for HIV during the cohort's sampling procedure. {[}Describe here what was done and when, which samples, which tissues{]}.

@@

Noticebly, bacterial community 15 consisted only of Lactobacillus species (\emph{Lactobacillus coleohominis, Lactobacillus crispatus/acidophilus, Lactobacillus iners, Lactobacillus jensenii, Lactobacillus reuteri/oris/frumenti/antri, other Lactobacillales, Ureaplasma parvum}).

Patients were thus subdivided into 6 groups,

@@

\includegraphics[width=1\linewidth]{manuscript_template_files/figure-latex/unnamed-chunk-3-1}

@@

\includegraphics[width=1\linewidth]{manuscript_template_files/figure-latex/unnamed-chunk-4-1}

@@

\includegraphics[width=1\linewidth]{manuscript_template_files/figure-latex/unnamed-chunk-6-1}

@@

@@

@@

>>>>

\title{Integrated multi-omics analysis reveals Lactobacillus anti-inflammatory process in vaginal tissue}
\usepackage{etoolbox}
\makeatletter
\providecommand{\subtitle}[1]{% add subtitle to \maketitle
  \apptocmd{\@title}{\par {\large #1 \par}}{}{}
}
\makeatother
\subtitle{A demonstration of Rmarkdown using Herman Bumpus' data}
\author{Author One\textsuperscript{1},
Author Two\textsuperscript{2},
Author Three\textsuperscript{1,2}}
\date{February 13, 2021}

@@

To understand the longitudinal and tissue-specific microbiome profile in vaginal samples, 111 adult female sex workers were enrolled in {[}\ldots{]}. Among those, 14 were previously tested positive for HIV during the cohort's sampling procedure. {[}Describe here what was done and when, which samples, which tissues{]}.

@@

Noticebly, bacterial community NA consisted only of Lactobacillus species (**).

Patients were thus subdivided into 8 groups,

@@

\includegraphics[width=1\linewidth]{manuscript_template_files/figure-latex/unnamed-chunk-5-1}

@@

\includegraphics[width=1\linewidth]{manuscript_template_files/figure-latex/unnamed-chunk-6-1}
\includegraphics[width=1\linewidth]{manuscript_template_files/figure-latex/unnamed-chunk-6-2}

@@

\includegraphics[width=1\linewidth]{manuscript_template_files/figure-latex/unnamed-chunk-8-1}

@@

\includegraphics[width=1\linewidth]{manuscript_template_files/figure-latex/unnamed-chunk-9-1}

@@

\includegraphics[width=1\linewidth]{manuscript_template_files/figure-latex/unnamed-chunk-10-1}

@@

\includegraphics[width=1\linewidth]{manuscript_template_files/figure-latex/unnamed-chunk-11-1}
\includegraphics[width=1\linewidth]{manuscript_template_files/figure-latex/unnamed-chunk-11-2}
\includegraphics[width=1\linewidth]{manuscript_template_files/figure-latex/unnamed-chunk-11-3}

\hypertarget{figure-s5}{%
\subsection{Figure S5}\label{figure-s5}}

\includegraphics[width=1\linewidth]{manuscript_template_files/figure-latex/unnamed-chunk-12-1}
\includegraphics[width=1\linewidth]{manuscript_template_files/figure-latex/unnamed-chunk-12-2}
\includegraphics[width=1\linewidth]{manuscript_template_files/figure-latex/unnamed-chunk-12-3}
